Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-30 draft/paper1_jenny.tex
Edit total stellar mass

    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
    stellar mass. 
    As expected, the integration of the 1-D profile out to very large radius recovers 
    more luminosity (stellar mass) compared to the \cmodel{}-based estimates 
    (Fig \ref{fig:mass_diff}).
    At high-\mstar{} end (e.g. \logmtot{}$>11.6$), the average difference is larger 
    than 0.1 dex and can be as large as 0.2--0.3 dex.  
    More importantly, the differences between \mtot{} and \mcmodel{} clearly show 
    dependence on total stellar mass as \mcmodel{} tends to misse more light in 
    more massive galaxies.  
    In the next section, we will show that this

    Our methodology ignores any radial variations in \m2l{}. 
    It is well known that massive ETGs have negative optical color gradients 
    indicating gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
    \citealt{DSouza2015}). \jenny{earlier reference here?}
    These color gradients are shallow and smooth out to a few times the effective 
    radius and color gradients at the outskirts are not yet well quantified.
    Our results looking at the outer envelopes as a function of mass and environment 
    will be robust as long as there is \emph{no significant difference in 
    the average color gradient between sub-samples}.
    %More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
    %our results will be robust as long as there is \emph{no significant difference in 
    %the average color gradient between the two samples}. 
    We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).

    Our method for deriving total stellar masses is similar to the 
    method adopted by the GAMA survey (\citealt{Taylor2011, Kelvin2012}). 
    We have compared our \mstar{} values with those from GAMA and the results are given 
    in Appendix~\ref{app:gama}. 
    We find a systematic differences between the two \mstar{} estimates.
    It is likely that the GAMA models fail to capture the flux associated with the 
    outskirts of galaxies due to the limited depth of SDSS.     
%% ------------------------------------------------------------------------------------ %%

>>>>

    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
    stellar mass. 
    As expected, the integration of the 1-D profile out to very large radius recovers 
    more luminosity (stellar mass) compared to the \cmodel{}-based estimates 
    (Fig \ref{fig:mass_diff}).
    At high-\mstar{} end (e.g. \logmtot{}$>11.6$), the average difference is larger 
    than 0.1 dex and can be as large as 0.2--0.3 dex.  
    More importantly, the differences between \mtot{} and \mcmodel{} clearly show 
    dependence on total stellar mass as \mcmodel{} tends to miss more light in 
    more massive galaxies.  
    This relates to the mass-dependence nature of the stellar halos in massive 
    galaxies and the intrinsic limitation of \cmodel{} method, which we will discuss
    more in the next section.
    Such differences also have important implications in the estimation of stellar 
    mass function or in the study of environment-dependence of galaxy structure.  
    We will also discuss these topics in Section \ref{sec:discussion}.

    Although 100 kpc is already a very large radius that should enclose the majority 
    of stars that belong to these massive galaxies, we know that their \mden{} 
    profiles extend beyond 100 kpc without showing sign of truncation. 
    Therefore, for massive galaxies, even \mtot{} should be only considered a lower
    limit of the ``total'' \mstar{}. 
    In Fig \ref{fig:mass_diff}, we also integrate the \mden{} of each galaxy to the 
    outermost radii as \mmax{} and compare their differences with \mtot{} 
    (right panel).  
    Although \mmax{} is much more uncertain than \mtot{} due to background subtraction
    and impacts from nearby objects, we see they do return more \mstar{} than \mtot{}. 
    However, the mass differences are on average very small ($\sim0.02-0.03$ dex) and 
    do not show strong mass dependence.  
    This confirms that, at the current depth of HSC images, \mtot{} can be used as 
    good proxy of ``total'' stellar mass.

    Our methodology ignores any radial variations in \m2l{}. 
    It is well known that massive ETGs have negative optical color gradients 
    indicating gradients in \m2l{} (e.g.\ \citealt{Carollo1993, Davies1993, 
    LaBarbera2012, DSouza2015}).
    These color gradients are shallow and smooth out to a few times the effective 
    radius and color gradients at the outskirts are not yet well quantified.
    Therefore, using average \m2l{} is unlikely to bias the results on \mstar{}
    measurements.  
    We will discuss color gradients more in Section~\ref{ssec:ell_color}. 
    In summary, we do not find optical color gradient shows dependence on stellar
    mass, hence the results about the mass-dependence of the \mden{} profiles will 
    not be affected by it.

    %Our results looking at the outer envelopes as a function of mass and environment 
    %will be robust as long as there is \emph{no significant difference in 
    %the average color gradient between sub-samples}.
    %We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).

    Our method for deriving total \mstar{} is similar to the method adopted by the 
    GAMA survey (\citealt{Taylor2011, Kelvin2012}), where the average \m2l{} is from 
    SED fitting of PSF-matched aperture photometry and the total luminosity comes from 
    sing-\ser{} modeling of the SDSS images. 
    To avoid the differences in stellar population assumptions, we directly compare the 
    total luminosity within 100 kpc and the GAMA single-\ser{} luminosity for the same
    galaxies. 
    At high-\mstar{} end, the HSC 1-D profiles still recover more light than the 
    single-\ser{} model on average.
    It is likely that the GAMA models fail to capture the flux associated with the 
    outskirts of galaxies due to the limited depth of SDSS.  
    Meanwhile, there are also many cases where the high-\ser{} index of GAMA model leads 
    to over-estimated total luminosity. 
    We will discuss more of this comparison in the next paper of this series 
    (Huang\etal in prep.).

    %We have compared our \mstar{} values with those from GAMA and the results are given 
    %in Appendix~\ref{app:gama}.
